Improving the Replicability of Psychological Science Through Pedagogy

### 2016-09-23 paper/paper.Rmd
eric suggestions

In the current work, we do not address these challenges directly; instead, our goal is more modest. We assess the probability that a graduate student can choose an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the findings. We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations. While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work.

@@

In sum, we view the contribution of the current work to be two-fold. First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom. Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced by a motivated student on a first attempt.

@@

>>>>

In the current work, we do not address these challenges; instead, our goal is more modest. We assess the probability that a graduate student can choose an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the findings. We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations. While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work. As we discuss below, these replications may have different interpretations: While some are more direct replication, others differ on theoretically-relevant dimensions. Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing boundary conditions of a particular effect. Even in these cases, however, our work provides contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.

@@

@@

One of the barriers to more reproducible work in psychology is pedagogical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners. Indeed, our students, who came from a variety of disciplinary backgrounds, had relatively little experience with web experiments or literate, reproducible data analysis. Yet by the end of the course, all had gained sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently. This experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environemnt -- students can quickly learn to use a reproducible toolset.
